### 2012-03-27 doc/theses/mikula/used_technologies_and_definitions.tex
Master thesis: Corrections.

\begin{figure}
\caption{A simple XML example}
\label{FIG_a_simple_xml_example}
\begin{verbatim}
<bookstore>
  <book id="b1">
    <title>
      Compilers: Principles, Techniques, and Tools
      (2nd Edition)
    </title>
    <authors>
      <author>Alfred V. Aho</author>
      <author>Monica S. Lam</author>
      <author>Ravi Sethi</author>
      <author>Jeffrey D. Ullman</author>
    </authors>
  </book>
  <book id="b2">
    <title>XQuery</title>
    <authors>
      <author>Priscilla Walmsley</author>
    </authors>
    <isbn>0596006349</isbn>
  </book>
</bookstore>
\end{verbatim}
\end{figure}
\todo[inline]{Zmensit Figure \ref{FIG_a_simple_xml_example}?}

@@

An example of DTD describing the book element from the XML example in Figure \ref{FIG_a_simple_xml_example} follows.

\todo[inline]{Toto do obrazku.}
\begin{verbatim}
<!ELEMENT book (title, authors, isbn?)>
<!ATTRLIST book id ID #REQUIRED>

@@

<!ELEMENT isbn #PCDATA>
\end{verbatim}

@@

The book element from the sample XML document in Figure \ref{FIG_a_simple_xml_example} can be described using the XSD as follows.

\todo[inline]{Do obrazku.}
\begin{alltt}
<xs:element name="book">
  <xs:complexType>
    <xs:sequence>
      <xs:element name="title" type="xs:string"/>
      <xs:element name="authors>
        <xs:complexType>
          <xs:element name="author" type="xs:string" maxOccurs="unbound"/>
        </xs:complexType>
      </xs:element>
      <xs:element name="isbn" type="xs:string" minOccurs="0"/>
    </xs:sequence>
    <xs:attribute name="id" type="xs:string" use="required"/>
  </xs:complexContent>
</xs:element>
\end{alltt}

>>>>

\begin{figure}
\begin{verbatim}
<bookstore>
  <book id="b1">
    <title>
      Compilers: Principles, Techniques, and Tools
      (2nd Edition)
    </title>
    <authors>
      <author>Alfred V. Aho</author>
      <author>Monica S. Lam</author>
      <author>Ravi Sethi</author>
      <author>Jeffrey D. Ullman</author>
    </authors>
  </book>
  <book id="b2">
    <title>XQuery</title>
    <authors>
      <author>Priscilla Walmsley</author>
    </authors>
    <isbn>0596006349</isbn>
  </book>
</bookstore>
\end{verbatim}
\caption{A simple XML example.}
\label{FIG_a_simple_xml_example}
\end{figure}

@@

An example of DTD describing the book element from the XML example in Figure \ref{FIG_a_simple_xml_example} is shown in Figure \ref{FIG_a_simple_dtd_example}.

\begin{figure}
\begin{verbatim}
<!ELEMENT book (title, authors, isbn?)>
<!ATTRLIST book id ID #REQUIRED>

@@

<!ELEMENT isbn #PCDATA>
\end{verbatim}
\caption{A simple DTD example.}
\label{FIG_a_simple_dtd_example}
\end{figure}

@@

The book element from the sample XML document in Figure \ref{FIG_a_simple_xml_example} can be described using the XSD as shown in Figure \ref{FIG_a_simple_xsd_example}.

\begin{figure}
\begin{alltt}
<xs:element name="book">
  <xs:complexType>
    <xs:sequence>
      <xs:element name="title" type="xs:string"/>
      <xs:element name="authors>
        <xs:complexType>
          <xs:element name="author" type="xs:string"
           maxOccurs="unbound"/>
        </xs:complexType>
      </xs:element>
      <xs:element name="isbn" type="xs:string" minOccurs="0"/>
    </xs:sequence>
    <xs:attribute name="id" type="xs:string" use="required"/>
  </xs:complexContent>
</xs:element>
\end{alltt}
\caption{A simple XSD example.}
\label{FIG_a_simple_xsd_example}
\end{figure}
